Universals of word order result from optimization of grammars for efficient communication

### 2019-03-13 second-draft/3-paper-names.tex
visualization

% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
\author[a,1,2]{Michael Hahn}
\author[a]{Daniel Jurafsky}
\author[b]{Richard Futrell}

\affil[a]{Stanford University}
\affil[b]{University of California, Irvine}

@@

\begin{abstract}
The universal properties of human languages have been the subject of intense study across disciplines. We report novel computational and corpus-based evidence for the hypothesis that a prominent subset of these universal properties---those related to word order---result from a process of optimization for efficient communication among humans. We develop a probabilistic, differentiable model of word order grammars: the means by which different languages convert underlying hierarchical structures into strings of words. We show how the parameters of a word order grammar can be optimized for efficiency of information transfer, quantified as a tradeoff between incremental predictability and mutual information with latent tree structures. Applying these grammars to tree structures found in dependency corpora from 51 languages, we show that optimizing the grammar parameters for efficiency results in word order patterns that reproduce a large subset of the major word order correlations reported in the linguistic typological literature, and reproduce the predictions of previous heuristic theories such as dependency length minimization.
\end{abstract}

@@

\dropcap{F}or decades, researchers in fields ranging from philology to cognitive science to statistical physics have been involved in documenting and trying to explain the universal syntactic and statistical properties of human language \cite{behaghel1909beziehungen,zipf1949human,greenberg1963universals,lin2017critical}. An explanation for the universal properties of language would enable a deeper scientific understanding of what human language is and how to model it, with applications in psychology and natural language processing \cite{hawkins2007processing,bender2009linguistically,bender2013linguistic}. In this work we examine this question from a computational perspective, demonstrating a fully formalized framework in which certain syntactic universals can be explained through the statistical optimization of grammars for information-theoretic efficiency. % TODO add a cogsci person to citation chain at the beginning

\textbf{TODO maybe should be more general in the beginning, as in the first version. Also make sure the reader doesn't think 'it's just headedness, why bother'.}

Natural languages vary a lot in the order in which they express information.
Consider Figure~\ref{fig:arabic-japanese-simple}, showing a sentence in Arabic (top) and Japanese (bottom), both translating to `I wrote a letter to a friend.'
Both sentences contain a verb meaning `wrote', a noun expressing  `letter', and a phrase translating to `to a friend'.
In linguistic terminology, `letter' is the object of the verb, whereas the phrases translating as `to a friend' are known as adpositional phrases.
While the two sentences containing words with the same meanings, the order of these words are entirely different in the two languages:
%However, the languages differ in the order in which these words and phrases are arranged: 
In Arabic, the verb stands at the beginning, followed by both the object and the adpositional phrase.
`To' is expressed by a \emph{preposition}, so named because it precedes the word expressing `friend'. %The adpositional phrase starts with the adposition.
In Japanese, the verb stands at the end; object and adpositional phrase precede it; `to' is expressed by a \textit{postposition}, so named because it follows the word denoting `friend'.
%What both languages have in common is that the object and the adpositional phrase stand on the same side of the verb, and that the objects of adpositions and verbs stand on the sam side of their heads.
%What both languages have in common is that the object and the adpositional phrase stand on the same side of the verb.
%It turns out that these are deep and stable regularities:
It turns out that this variation reflects a deep and stable regularity:
While languages ordering the objects before (Japanese) or after (Arabic) the verb are approximately equally common around the world,
this is strongly correlated with the occurrence of pre- or postpositions:
Languages ordering their objects the way Japanese does, have postpositions; languages ordering them as Arabic does have prepositions.
%However, the vast majority of natural languages place adpositional phrases on the same side of the verb as the object:
This correlation has an extremely strong empirical basis:
In a sample of about 1,100 languages from five contents (CITE Dryer WALS 95a), less than 7 \% of languages provide clear exceptions to this generalization. %, over 90 \% of languages satisfy this generalization .

This generalization falls in a group of language universals that were originally documented by Greenberg \cite{greenberg1963universals}, known as \key{word order correlations}:
These describe correlations between the relative positions of different types of expressions across languages.
The example above documents that the position of the object (`letter') relative to the verb is \key{correlated} with the position of the adposition (`to'). %adpositional phrases (`to a friend') relative to the verb.
Greenberg originally worked with 30 languages; the correlation universals have since been confirmed on the basis of much larger samples of languages.
The authoritative study by Dryer \cite{dryer1992greenbergian} draws on 625 languages and documents fifteen such correlations.
%For instance, the relative order of objects and nouns also strongly determines the positions of genitives, auxiliaries, and other

%These universals are supported by languages on all five continents, cutting across language families.

%These cross-linguistic patterns call for an explanation, and 
%and the problem of explaining the word order correlations has inspired a long tradition of research.
Supported by languages on all continents, these correlations are among the language universals with the strongest empirical support.
Importantly, their validity is also independent from specific assumptions about theories of grammar.

Consequently, explaining these patterns has been an important aim of linguistic research since Greenberg's seminal study.
%
%%supported by languages on all continents, and their validity is independent from 
%
%TODO say more about why these are extremely important, and that it is a puzzle why they are true
%
%%An explanation for the universal properties of language would enable a deeper scientific understanding of what human language is and how to model it, with applications in psychology and natural language processing \cite{hawkins2007processing,bender2009linguistically,bender2013linguistic}. 
%
A prominent line of research has argued that universals arise for \key{functional} reasons: that is, because they make human communication and language processing maximally efficient, and regularities across languages hold because these efficiency constraints are rooted in general principles of communication and cognition (e.g., \cite{gabelentz1901sprachwissenschaft,zipf1949human,hockett1960origin,givon1991markedness,hawkins1994performance,hawkins2004efficiency,hawkins2014crosslinguistic,croft2001functional,haspelmath2008parametric,jaeger2011language}).
Under this view, the various human languages represent multiple solutions to the problem of efficient information transfer given human cognitive constraints.

@@

A commonly proposed functional explanation of Greenberg's correlations is in terms of Dependency Length Minimization \cite{futrell2015largescale,liu2017dependency,temperley2018minimizing}.
This is the idea that languages order words so as to minimize the linear distance between words linked in head--dependent relationships.
This has been confirmed on the basis of large-scale corpus evidence \cite{futrell2015largescale,liu2017dependency,temperley2018minimizing}, and has been justified based on the reasoning that long dependencies create high memory requirements for parsing and generation \cite{gibson1998linguistic,gibson2000dependency}.

%In previous studies of word order optimization, it has been common to propose that word orders are chosen to minimize \key{dependency length}, the linear distance between words linked in head--dependent relationships \cite{futrell2015largescale,liu2017dependency,temperley2018minimizing}. 
%Dependency length has been proposed as a metric of processing difficulty on the reasoning that long dependencies create high memory requirements for parsing and generation \cite{gibson1998linguistic,gibson2000dependency}, and minimization of dependency length is known to recover a large subset of the Greenbergian universals \cite{hawkins1994performance,hawkins2004efficiency,hawkins2014crosslinguistic}. 
%We demonstrate that the minimization of dependency length can be formalized in our framework, reproducing the finding that optimizing grammars for dependency length recovers several word order universals \cite{gildea2010grammars}.

Zipf \cite{zipf1949human} argued that language optimizes a tradeoff between speaker effort (Force of Unification) and listener effort (Force of Diversification).
According to this theory, a language that minimizes speaker effort should reduce the number of different utterances to make production as easy as possible.
Conversely, to minimize listener effort, the language should provide different utterances for different meanings, so that the listeenr can unambiguously identify the meaning from the utterance.
Minimizing speaker and listener effort represent two opposing forces:
A pressure to reduce the complexity of the language makes the utterances in a language more homogenous.
A pressure to reduce ambiguity makes utterances more heterogeneous, so they can indicate different meanings.
%Another way to conceptualize these two pressures is as the \key{cost} and \key{informativity} of language use:
Producing and processing simple utterances incurs little cost, but more complex and diverse utterances are required to be provide higher informativity.
The idea that language results from the tension between these two pressures has a long and fruitful history.
%\cite{horn-toward-1984}, RSA, Color naming
%
%In the domain of word order, 
%
%TODO introduce the terms \key{cost} and \key{informativity}
%
This idea has been shown to account for phenomena such as pragmatic inference \cite{horn-toward-1984, frank2012predicting} and color naming~\cite{zaslavsky2018efficient}.

@@

In this work, we show that the word order of languages has evolved to optimize efficiency, and that efficiency optimization accounts for the Greenbergian word order correlations.

%In this work, we show computationally, using corpus data from 51 languages, that efficiency optimization accounts for the Greenbergian word order correlations.
That is, we show that the word orders in natural languages have evolved to optimize efficiency, and that this optimization accounts for the prevalence of the word order correlations. %word orders in natural language

@@

\begin{table*}
	\begin{center}
\begin{tabular}{|ll|l|l|l|ll|l|llllllll}
	\hline
	%&
	\multicolumn{2}{|c|}{Correlates with...}   &         \multirow{2}{*}{Real}   & \multirow{2}{*}{DepL}  & \multirow{2}{*}{Pred}   &  \multirow{2}{*}{Pars} &  \multirow{2}{*}{Efficiency}  \\ 
	verb & object     & & & &  & \\ \hline \hline % \textsc{verb} $\xrightarrow{obj}$ \textsc{noun}
%adp. &
	adposition    &    NP       \\
	\emph{to}            & \emph{a friend} \\
copula    &    NP        &     \\
	\emph{is}        & \emph{a friend} \\
auxiliary    &    VP       &   \\
	\emph{has}          & \emph{written} \\
noun    &    genitive      &  \\
	\emph{friend} &  \emph{of John} \\
noun    &    relative clause       &  \\
	\emph{books} & \emph{that you read} \\
complementizer    &    S        & \\
	\emph{that} & \emph{Mary} \\
verb    &    PP     &    \\
	\emph{went} & \emph{to school} \\
want    &    VP      &    \\
	\emph{wants}   &  \emph{to leave} \\
verb    &    subject    &  \\
	\emph{(there) entered} & \emph{a person} \\
verb    &    manner adverb     & \\
	\emph{ran} & \emph{quickly} \\
 \hline
%comp. &
%\multirow{3}{*}{NP}&
%	AP &
    \multicolumn{6}{l}{\footnotesize{Significance levels: $^*$: $p < 0.05$, $^{**}$: $p < 0.01$, $^{***}$: $p < 0.001$}}
\end{tabular}
	\end{center}
	\caption{Greenbergian Correlations. Following \cite{dryer1992greenbergian}, each correlation is stated in terms of a pair of a `verb patterner' and an `object patterner', whose relative order correlate with that of verbs and objects.
For each correlation, we provide an example.
Given the statistical nature of the correlations, not every language satisfies every one of them.
Not all correlations are satisfied by every natu
}\label{table:corr-dryer}
\end{table*}

>>>>

% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
%\author[a,1,2]{Michael Hahn}
%\author[a]{Daniel Jurafsky}
%\author[b]{Richard Futrell}

%\affil[a]{Stanford University}
%\affil[b]{University of California, Irvine}

@@

\begin{abstract}
	TODO rewrite
The universal properties of human languages have been the subject of intense study across disciplines.
	We report novel computational and corpus-based evidence for the hypothesis that a prominent subset of these universal properties---those related to word order---result from a process of optimization for efficient communication among humans.
	TODO explain
	%We develop a probabilistic, differentiable model of word order grammars: the means by which different languages convert underlying hierarchical structures into strings of words.
	%We show how the parameters of a word order grammar can be optimized for efficiency of information transfer, quantified as a tradeoff between incremental predictability and mutual information with latent tree structures.
	Applying these grammars to tree structures found in dependency corpora from 51 languages, we show that optimizing the grammar parameters for efficiency results in word order patterns that predict a large subset of the major word order correlations reported in the linguistic typological literature, and subsumes the predictions of previous heuristic theories such as dependency length minimization.
\end{abstract}

@@

\dropcap{F}or TODO rewrite first sentence. decades, researchers in fields ranging from philology to cognitive science to statistical physics have been involved in documenting and trying to explain the universal syntactic and statistical properties of human language \cite{behaghel1909beziehungen,zipf1949human,greenberg1963universals,lin2017critical}. An explanation for the universal properties of language would enable a deeper scientific understanding of what human language is and how to model it, with applications in psychology and natural language processing \cite{hawkins2007processing,bender2009linguistically,bender2013linguistic}. In this work we examine this question from a computational perspective, demonstrating a fully formalized framework in which certain syntactic universals can be explained through the statistical optimization of grammars for information-theoretic efficiency. % TODO add a cogsci person to citation chain at the beginning

%\textbf{TODO maybe should be more general in the beginning, as in the first version. Also make sure the reader doesn't think 'it's just headedness, why bother'.}

Natural languages vary a lot in the order in which they express information.
Consider Figure~\ref{fig:arabic-japanese-simple}, showing a sentence in Arabic (top) and Japanese (bottom), both translating to `I wrote a letter to a friend.'
Both sentences contain a verb meaning `wrote', a noun expressing  `letter', and a phrase translating to `to a friend'.
In linguistic terminology, `letter' is the object of the verb, whereas the phrases translating as `to a friend' are known as adpositional phrases.
While the two sentences containing words with the same meanings, the order of these words are entirely different in the two languages:
%However, the languages differ in the order in which these words and phrases are arranged: 
In Arabic, the verb stands at the beginning, followed by both the object and the adpositional phrase.
`To' is expressed by a \emph{preposition}, so named because it precedes the word expressing `friend'. %The adpositional phrase starts with the adposition.
In Japanese, the verb stands at the end; object and adpositional phrase precede it; `to' is expressed by a \textit{postposition}, so named because it follows the word denoting `friend'.
%What both languages have in common is that the object and the adpositional phrase stand on the same side of the verb, and that the objects of adpositions and verbs stand on the sam side of their heads.
%What both languages have in common is that the object and the adpositional phrase stand on the same side of the verb.
%It turns out that these are deep and stable regularities:
It turns out that this variation reflects a deep and stable regularity:
While languages ordering the objects before (Japanese) or after (Arabic) the verb are approximately equally common around the world,
this is strongly correlated with the occurrence of pre- or postpositions (Figure~\ref{fig:corr-table}, top):
Languages ordering their objects the way Japanese does, have postpositions; languages ordering them as Arabic does have prepositions.
%However, the vast majority of natural languages place adpositional phrases on the same side of the verb as the object:
%As Figure~\ref{fig:corr-table} shows, this correlation has an extremely strong empirical basis:
%In a sample of about 1,100 languages from five contents (CITE Dryer WALS 95a), less than 7 \% of languages provide clear exceptions to this generalization. %, over 90 \% of languages satisfy this generalization .

\begin{figure}
    \centering
    \includegraphics[width=0.4\textwidth]{figures/corr-full.png}
%
%\centering
%\begin{dependency}[theme = simple]
%   \begin{deptext}[column sep=1em]
%%	   I \& wrote \& the \& letter \& in \& Japanese \& . \\
%	   katabt \& risāla \& li \& sadīq  \\
%%	   \textsc{verb} \& \textsc{noun} \& \textsc{adp} \& \textsc{noun} \\
%	   wrote \& letter   \& to \& friend  \\
%   \end{deptext}
%\end{dependency}
%\begin{dependency}[theme = simple]
%   \begin{deptext}[column sep=1em]
%      tomodachi \& ni \& tegami-o \& kaita \\
% %\textsc{noun} \& \textsc{adp} \& \textsc{noun} \& \textsc{verb}\\
%	   friend \& to \& letter  \& wrote \\
%   \end{deptext}
%\end{dependency}
%
%    \centering
%    \includegraphics[width=0.4\textwidth]{figures/corr-table.png}
%
%%\begin{dependency}[theme=simple]
%%    \begin{deptext}
%%    I \& wrote \& a \& letter \& to \& a \& friend \\
%%    \end{deptext}
%%    \depedge{2}{1}{nsubj}
%%    \depedge{2}{4}{obj}
%%    \depedge{4}{3}{ }
%%    \depedge{4}{3}{ }
%%    \depedge{2}{5}{}
%%    \depedge{5}{7}{ }
%%    \depedge{7}{6}{ }
%%\end{dependency}
	\caption{ The concept of a word order correlation: Languages can order the object after (Arabic) or before (Japanese) the verb, and have prepositions (Arabic) or postpositions (Japanese). For each combination, we indicate how many languages satisfy it, as documented in the World Atlas of Language Structure~\cite{wals}. Combinations on the diagonal are vastly more common than off-diagonal ones. % A sentence in Arabic (top) and Japanese (bottom), translating to `I wrote a letter to a friend.' Note the reversal of word order: Arabic has verb-object order and prepositions, while Japanese has object-verb order and postpositions.
	}\label{fig:arabic-japanese-simple}	\label{fig:corr-table}
\end{figure}

This generalization falls in a group of language universals that were originally documented by Greenberg \cite{greenberg1963universals}, known as \key{word order correlations}:
These describe correlations between the relative positions of different types of expressions across languages.
The example above documents that the position of the object (`letter') relative to the verb is \key{correlated} with the position of the adposition (`to'). %adpositional phrases (`to a friend') relative to the verb.
Greenberg originally worked with 30 languages; the correlation universals have since been confirmed on the basis of much larger samples of languages.
The authoritative study by Dryer \cite{dryer1992greenbergian} draws on 625 languages and documents fifteen such correlations.

Supported by languages on all continents, these correlations are among the language universals with the strongest empirical support.
Importantly, their validity is also independent from specific assumptions about theories of grammar.

Consequently, explaining these patterns has been an important aim of linguistic research since Greenberg's seminal study.
An explanation for the universal properties of language would enable a deeper scientific understanding of what human language is and how to model it, with applications in psychology and natural language processing \cite{hawkins2007processing,bender2009linguistically,bender2013linguistic}.

A prominent line of research has argued that universals arise for \key{functional} reasons: that is, because they make human communication and language processing maximally efficient, and regularities across languages hold because these efficiency constraints are rooted in general principles of communication and cognition (e.g., \cite{gabelentz1901sprachwissenschaft,zipf1949human,hockett1960origin,givon1991markedness,hawkins1994performance,hawkins2004efficiency,hawkins2014crosslinguistic,croft2001functional,haspelmath2008parametric,jaeger2011language}).
Under this view, the various human languages represent multiple solutions to the problem of efficient information transfer given human cognitive constraints.

@@

Prior studies of word order typology have proposed Dependency Length Minimization (DLM) as general principle of word order \cite{futrell2015largescale,liu2017dependency,temperley2018minimizing}.
This is the idea that languages order words so as to minimize the linear distance between words linked in grammatical relationships.
This principle is a heuristic formalization of the idea that long dependencies should create high memory requirements in language processing \cite{gibson1998linguistic,gibson2000dependency}.
Cross-linguistic corpus studies have shown that languages do minimize dependency length beyond chance, suggesting that DLM is a language universal \cite{futrell2015largescale,liu2017dependency,temperley2018minimizing}.
It has also been argued theoretically that this principle should account for Greenberg's correlations, though this link is nontrivial and depends on the precise distributions of tree topologies in syntactic structures.
As a principle of word order, DLM is also stipulative: There are other processing models, such as surprisal, that are strongly predictive of human processing cost, and make predictions distinct from, and partly conflicting with, those of DLM~\cite{hale2001probabilistic,levy2008expectation}.

Zipf \cite{zipf1949human} argued that language optimizes a tradeoff between the Forces of Unification and Diversification.
The Force of Unification is a pressure to reduce the complexity of the language to make production and processing as easy as possible.
Conversely, the Force of Diversification favors languages that provide different utterances for different meanings, so that the listener can unambiguously identify the meaning from the utterance.
%Minimizing speaker and listener effort represent two opposing forces:
%A pressure to reduce the complexity of the language makes the utterances in a language more homogenous.
%A pressure to reduce ambiguity makes utterances more heterogeneous, so they can indicate different meanings.
%Another way to conceptualize these two pressures is as the \key{cost} and \key{informativity} of language use:
These two forces act in opposing directions:
Producing and processing simple utterances incurs little cost, but more complex and diverse utterances are required to be provide higher informativity.
The idea that language results from the tension between these two pressures has a long and fruitful history.
%\cite{horn-toward-1984}, RSA, Color naming
%
%In the domain of word order, 
%
%TODO introduce the terms \key{cost} and \key{informativity}
%
This idea has been shown to provide a formalization and derivation of pragmatic inference \cite{horn-toward-1984, frank2012predicting}.
It also has been shown to account for the distribution of word meanings across languages, such as color naming~\cite{zaslavsky2018efficient}.

%

%
%

@@

In this work, we first provide a formalization of efficiency in the domain of word order, drawing on information-theoretic notions.
We then show that the word order of languages has evolved to optimize efficiency, and that efficiency optimization accounts both for the Greenbergian word order correlations and for Dependency Length Minimization.

%In this work, we show computationally, using corpus data from 51 languages, that efficiency optimization accounts for the Greenbergian word order correlations.
%That is, we show that the word orders in natural languages have evolved to optimize efficiency, and that this optimization accounts for the prevalence of the word order correlations. %word orders in natural language

%OR say DLM and efficiency, as in the talks

@@

%
%
%\begin{table}
%	\begin{center}
%%		\setlength\tabcolsep{1.5pt}
%\begin{tabular}{|ll|c|cccc|llllllll}
%	\hline
%	%&
%	\multicolumn{2}{|c|}{Correlates with...}   &         \multirow{2}{*}{Real}   & \multirow{2}{*}{DepL}  & \multirow{2}{*}{Pred}   &  \multirow{2}{*}{Pars} &  \multirow{2}{*}{Eff}  \\ 
%	verb & object     & & & &  & \\ \hline \hline % \textsc{verb} $\xrightarrow{obj}$ \textsc{noun}
%%adp. &
%	adposition    &    NP       
%	& \multirow{2}{*}{\includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-ground-lifted_case.pdf} } %\textbf{86}  }
%	&   \multirow{2}{*}{ \includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-depl-lifted_case.pdf}       }
%	&    \multirow{2}{*}{\includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-langmod-lifted_case.pdf} } %  \textbf{47 \%}$^{}$   }
%	&    \multirow{2}{*}{\includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-parser-lifted_case.pdf}   }   
%	&   \multirow{2}{*}{  \includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-efficiency-lifted_case.pdf}     }  \\
%	\emph{to}            & \emph{a friend} &&&&&\\ \hline
%copula    &    NP         
%	&  \multirow{2}{*}{\includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-ground-lifted_cop.pdf} }% \textbf{94} }
%	&   \multirow{2}{*}{ \includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-depl-lifted_cop.pdf}       }
%	&    \multirow{2}{*}{\includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-langmod-lifted_cop.pdf} } % \textbf{53}     }
%	&   \multirow{2}{*}{  \includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-parser-lifted_cop.pdf}   }   
%	&   \multirow{2}{*}{  \includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-efficiency-lifted_cop.pdf}   }  \\
%	\emph{is}        & \emph{a friend}  &&&&&\\ \hline
%auxiliary    &    VP       
%	&  \multirow{2}{*}{\includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-ground-aux.pdf}}
%	&   \multirow{2}{*}{ \includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-depl-aux.pdf}       }
%	&    \multirow{2}{*}{\includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-langmod-aux.pdf}     }
%	&   \multirow{2}{*}{ \includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-parser-aux.pdf}  }   
%	&   \multirow{2}{*}{  \includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-efficiency-aux.pdf}  }  \\
%	\emph{has}          & \emph{written}  &&&&&\\ \hline
%noun    &    genitive      
%	&  \multirow{2}{*}{\includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-ground-nmod.pdf}}
%	&   \multirow{2}{*}{ \includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-depl-nmod.pdf}     }
%	&    \multirow{2}{*}{\includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-langmod-nmod.pdf}   }
%	&   \multirow{2}{*}{ \includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-parser-nmod.pdf}  }   
%	&   \multirow{2}{*}{  \includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-efficiency-nmod.pdf}  }  \\
%	\emph{friend} &  \emph{of John}  &&&&&\\ \hline
%noun    &    relative clause      
%	&  \multirow{2}{*}{\includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-ground-acl.pdf}}
%	&   \multirow{2}{*}{  \includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-depl-acl.pdf}     }
%	&    \multirow{2}{*}{\includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-langmod-acl.pdf}   }
%	&   \multirow{2}{*}{ \includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-parser-acl.pdf}  }   
%	&   \multirow{2}{*}{  \includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-efficiency-acl.pdf}  }  \\
%	\emph{books} & \emph{that you read}  &&&&&\\ \hline
%complementizer    &    S        
%	&  \multirow{2}{*}{\includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-ground-lifted_mark.pdf}}
%	&   \multirow{2}{*}{ \includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-depl-lifted_mark.pdf}     }
%	&    \multirow{2}{*}{\includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-langmod-lifted_mark.pdf}     }
%	&   \multirow{2}{*}{  \includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-parser-lifted_mark.pdf} }   
%	&   \multirow{2}{*}{  \includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-efficiency-lifted_mark.pdf}  }  \\
%	\emph{that} & \emph{she has arrived}  &&&&&\\ \hline
%verb    &    PP         
%	&  \multirow{2}{*}{\includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-ground-obl.pdf}}
%	&   \multirow{2}{*}{ \includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-depl-obl.pdf}     }
%	&    \multirow{2}{*}{\includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-langmod-obl.pdf}     }
%	&   \multirow{2}{*}{  \includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-parser-obl.pdf} }   
%	&   \multirow{2}{*}{  \includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-efficiency-obl.pdf}  }  \\
%	\emph{went} & \emph{to school}  &&&&&\\ \hline
%want    &    VP        
%	&  \multirow{2}{*}{\includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-ground-xcomp.pdf}}
%	&   \multirow{2}{*}{ \includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-depl-nmod.pdf}     }
%	&    \multirow{2}{*}{\includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-langmod-xcomp.pdf}     }
%	&   \multirow{2}{*}{ \includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-parser-nmod.pdf}  }   
%	&   \multirow{2}{*}{  \includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-efficiency-xcomp.pdf}  }  \\
%	\emph{wants}   &  \emph{to leave}  &&&&&\\ \hline
% \hline
%%comp. &
%%\multirow{3}{*}{NP}&
%%	AP &
%    \multicolumn{6}{l}{\footnotesize{Significance levels: $^*$: $p < 0.05$, : $p < 0.01$, : $p < 0.001$}}
%\end{tabular}
%	\end{center}
%	\caption{Greenbergian Correlations. Each correlation is stated in terms of a pair of a `verb patterner' and an `object patterner', whose relative order correlate with that of verbs and objects.
%For each correlation, we provide an English example.
%%Given the statistical nature of the correlations, not every language satisfies every one of them.
%%Not all correlations are satisfied by every natu
%}\label{table:corr-dryer}
%\end{table}
%
%

%
%
%\begin{table*}
%	\begin{center}
%\begin{tabular}{|ll|l|l|l|ll|l|llllllll}
%	\hline
%	%&
%	\multicolumn{2}{|c|}{Correlates with...}   &         \multirow{2}{*}{Real}   & \multirow{2}{*}{DepL}  & \multirow{2}{*}{Pred}   &  \multirow{2}{*}{Pars} &  \multirow{2}{*}{Efficiency}  \\ 
%	verb & object     & & & &  & \\ \hline \hline % \textsc{verb} $\xrightarrow{obj}$ \textsc{noun}
%%adp. &
%	adposition    &    NP       
%	&  \multirow{2}{*}{\includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-ground-lifted_case.pdf} } %\textbf{86}  }
%	&   \multirow{2}{*}{ \includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-depl-lifted_case.pdf}   $^{***}$    }
%	&    \multirow{2}{*}{\includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-langmod-lifted_case.pdf} } %  \textbf{47 \%}$^{}$   }
%	&    \multirow{2}{*}{\includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-parser-lifted_case.pdf}  $^{***}$ }   
%	&   \multirow{2}{*}{  \includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-efficiency-lifted_case.pdf} $^{***}$    } \\
%	\emph{to}            & \emph{a friend} \\ \hline
%copula    &    NP         
%	&  \multirow{2}{*}{\includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-ground-lifted_cop.pdf} }% \textbf{94} }
%	&   \multirow{2}{*}{ \includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-depl-lifted_cop.pdf}   $^{***}$    }
%	&    \multirow{2}{*}{\includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-langmod-lifted_cop.pdf} } % \textbf{53}     }
%	&   \multirow{2}{*}{  \includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-parser-lifted_cop.pdf}  $^{***}$ }   
%	&   \multirow{2}{*}{  \includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-efficiency-lifted_cop.pdf} $^{**}$  }  \\
%	\emph{is}        & \emph{a friend} \\ \hline
%auxiliary    &    VP       
%	&  \multirow{2}{*}{\includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-ground-aux.pdf}}
%	&   \multirow{2}{*}{ \includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-depl-aux.pdf}   $^{***}$    }
%	&    \multirow{2}{*}{\includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-langmod-aux.pdf}  $^{***}$   }
%	&   \multirow{2}{*}{ \includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-parser-aux.pdf}  }   
%	&   \multirow{2}{*}{  \includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-efficiency-aux.pdf}$^{**}$  }  \\
%	\emph{has}          & \emph{written} \\ \hline
%noun    &    genitive      
%	&  \multirow{2}{*}{\includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-ground-nmod.pdf}}
%	&   \multirow{2}{*}{ \includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-depl-nmod.pdf} $^{***}$    }
%	&    \multirow{2}{*}{\includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-langmod-nmod.pdf}   }
%	&   \multirow{2}{*}{ \includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-parser-nmod.pdf} $^{***}$ }   
%	&   \multirow{2}{*}{  \includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-efficiency-nmod.pdf}$^{***}$  }  \\
%	\emph{friend} &  \emph{of John} \\ \hline
%noun    &    relative clause      
%	&  \multirow{2}{*}{\includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-ground-acl.pdf}}
%	&   \multirow{2}{*}{  \includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-depl-acl.pdf} $^{***}$    }
%	&    \multirow{2}{*}{\includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-langmod-acl.pdf}   }
%	&   \multirow{2}{*}{ \includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-parser-acl.pdf} $^{**}$ }   
%	&   \multirow{2}{*}{  \includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-efficiency-acl.pdf}$^{***}$  }  \\
%	\emph{books} & \emph{that you read} \\ \hline
%complementizer    &    S        
%	&  \multirow{2}{*}{\includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-ground-lifted_mark.pdf}}
%	&   \multirow{2}{*}{ \includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-depl-lifted_mark.pdf} $^{***}$    }
%	&    \multirow{2}{*}{\includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-langmod-lifted_mark.pdf}  $^{**}$   }
%	&   \multirow{2}{*}{  \includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-parser-lifted_mark.pdf}$^{***}$ }   
%	&   \multirow{2}{*}{  \includegraphics[width=0.03\textwidth]{../results/correlations/figures/correlations/correlation-efficiency-lifted_mark.pdf}$^{**}$  }  \\
%	\emph{that} & \emph{Mary has arrived} \\ \hline
%verb    &    PP         
